Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
d

**Idea**: study early modern knowledge production, all of it (1470-1830)

@@

### Peaks and drops – role of publishers and contingency

@@

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/LIBER-13-2.png
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption (km2)")
  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
  print(p)
}
```

@@

Proportions for title count, paper, and publishers

```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=8}
pics <- list()
for (catalogue in na.omit(unique(df0$catalog))) {

@@

### Development of number of publishers in Finland

@@

### Number of publishers in Stockholm 1760-1770

```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
sel.years = c(1760, 1780)
pics <- list()

@@

### Different languages in Swedish University towns

```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}
pics <- list()
theme_set(theme_bw(20))
myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")

@@

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]],
             pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], 
             nrow = 3)
```

@@

### Topic diversity in different languages in Finnish publications
TODO: TÄMÄ PITÄISI RAJATA LOPPUMAAN VUOTEEN 1828.
LL: on rajattu jo mun nähdäkseni ?

@@

### Combining devotional literature and temporary sermons

@@

##TODO: Dissertation language

@@

TODO: OISKO NÄMÄ VIELÄ SELVEMPIÄ VÄRIKKÄINÄ BARPLOTTEINA?

@@

TODO: KUVA PITÄIS RAJATA 1640-1828, EN ONNISTUNUT - DONE

@@

TODO: General analysis (any simple picture) of duplicates between Kungliga and Fennica based on Hege's deduplication code.

>>>>

**Idea**: to study early modern knowledge production, all of it (1470-1830)

@@

### Peaks and drops – role of publishers and contingency
TODO: Tuolla on yksi iso piikki Kungligassa (1760-1770) ja kaksi laskua Fennicassa (1700-1721) ja (1809-1828). Voisko ne HIGHLIGHTata jollain tyylikkäällä tavalla?

@@

TODO: Tässä vois maalata ton octavo-kirjojen käyrän molemmista kuvista jollain kirkkaalla värillä (ei muuta).
```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/LIBER-13-2.png
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption (km2)")
  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
  print(p)
}
```

@@

Proportions for title count, paper, and publishers
TODO: OTHER julkaisijakenttä laittaa ton Turku-kuvan pieleen, "other" kategoria liian iso.
```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=8}
pics <- list()
for (catalogue in na.omit(unique(df0$catalog))) {

@@

### Development of number of publishers in Finland 
TODO: Voisko tämän ja seuraavan kuvan (ruotsalaiset julkaisijat) jotenkin yhdistää järkevästi selvyyden vuoksi? En valitettavasti tiedä miten se teknisesti tehtäisiin.

@@

### Number of publishers in Stockholm 1760-1770
TODO: Tästä kaikki Fennica kuvat pois analyysistä selkeyden vuoksi.
```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
sel.years = c(1760, 1780)
pics <- list()

@@

### Different languages in Turku, Stockholm and Uppsala
TODO: Rajataan analyysi Turku (Fennica), Stockholm (Kungliga) ja Uppsala (Kungliga)
```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}
pics <- list()
theme_set(theme_bw(20))
myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")

@@

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]],
             pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], 
             nrow = 2)
```

@@

### Topic diversity in different languages in Finnish publications

@@

### Combining devotional literature and temporary sermons
TODO: Voisko kokeilla tätä barplotteina selvyyden vuoksi?

@@

###TODO: Dissertation language

@@

@@

TODO: kuva rajattu 1640-1828, MUTTA piirtää silti tuonne nuo tyhjät vuodet 1470-1640. NE PITÄIS SAADA PRINTISTÄ POIS.

@@
